Hysteresis in human computation:\\ how one task affects another

### 2014-11-26 docs/publications/2014.09_SCIENCE/man.tex
improve .gitignore

\subsection*{S3: Additional results not shown in the main text}
\begin{itemize}
	\item{
		the top 5 most suppressed and most activated terms between treatment
		pairs.
	}
\end{itemize}

@@

\subsection*{S8: Measuring computational hysteresis}
\begin{itemize}
	\item{principled use of cross-validation without optimization.}
	\item{Adopting Naive Bayes due to the lack of optimization required.}
	\item{
		Usage of a principled set of pre-processing and representation 
		techniques.
	}
	\item{
		Comparison to other choices of representation
	}
	\item{
		Comparison to SVM classifier
	}
	\item{
		Reiterate why we cannot report optimized results.
	}
\end{itemize}

>>>>

\subsection*{S3: Additional results not shown in the main text}
		the top 5 most suppressed and most activated terms between treatment
		pairs.

\begin{table}
	\centering
	\setlength{\tabcolsep}{10pt}
	\begin{tabular}{ c c c c c }

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{task1}} \\
		\toprule
		coffee & 38 \\
		meal & 34 \\
		cheese & 34 \\
		apple & 32 \\
		dessert & 21 \\
		cup & -30 \\
		glass & -45 \\
		table & -70 \\
		candle & -74 \\
		food & -80 \\
		\bottomrule
		\end{tabular}

&

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{frame1}} \\
		\toprule
		bread & 18 \\
		wine & 18 \\
		cheese & 16 \\
		apple & 14 \\
		oil & 12 \\
		table & -9 \\
		meal & -10 \\
		candle & -12 \\
		dinner & -13 \\
		food & -32 \\
		\bottomrule
		\end{tabular}

&

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{echo}} \\
		\toprule
		apple & 24 \\
		cheese & 23 \\
		wine & 15 \\
		coffee & 14 \\
		oil & 7 \\
		knife & -24 \\
		dinner & -26 \\
		fork & -27 \\
		candle & -35 \\
		food & -55 \\
		\bottomrule
		\end{tabular}

&

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{task2}} \\
		\toprule
		spicy & 26 \\
		sauce & 17 \\
		indian & 15 \\
		buffet & 14 \\
		exotic & 12 \\
		festival & -11 \\
		offering & -12 \\
		statue & -15 \\
		india & -20 \\
		food & -56 \\
		\bottomrule
		\end{tabular}

&

		\setlength{\tabcolsep}{4pt}
		\begin{tabular}{ r | c }
		\toprule
		\multicolumn{2}{c}{\textit{frame2}} \\
		\toprule
		indian & 11 \\
		banquet & 8 \\
		spicy & 7 \\
		asian & 6 \\
		variety & 6 \\
		delicious & -6 \\
		meat & -7 \\
		festival & -7 \\
		spice & -7 \\
		food & -9 \\
		\bottomrule
		\end{tabular}

	\end{tabular}
	\caption{blah}
\end{table}

@@

\subsection*{S8: Measuring computational hysteresis}
\begin{itemize}
	\paragraph{Using cross-validation accuracy to lower-bound L1-distance.}
	In order for Eq.~\ref{l1} to be applicable, it is necessary to obtain
	an unbiased estimate of a classifier's performance.  One well-known
	pitfall in measuring this error is to underestimate it due to 
	over-fitting of the data used.  As an example, if one were to try 
	a large number of classifiers, eventually one would find one that
	classifies the data perfectly, even though it might non generalize to
	new data.

	It is customary to use part of a data set to optimize hyperparameters of
	a model, and then test the model on as-yet unseen data.  In our case,
	don't have enough samples in each treatment to do this.  Instead, for 
	this reason, we make principled decisions for all of the options used
	in our classifier, and then test it's accuracy using cross validation,
	with no optimization performed on the data.  It was cruicial for 
	the statistical validity of our approach that we test our classifier on 
	each datum only once, and report these results without any optimizations
	of the classifier.

	In performing the classification we had various options, and since we
	could not optimize these choices, we made principled decisions based on
	prior knowledge from text classification applications.  We describe the
	options we faced and the choices we made below.

	\textit{whether to correct misspelled words.}  Because we used free-text
	entry for the labels, there was bound to be many spelling mistakes.
	This would tend to reduce the accuracy of a classifier, because the 
	entries ``bread'' and ``braed'' would be regarded as completely different
	features, even though they clearly correspond to the same 
	\textit{intended word}.  While no algorithm can determine a worker's 
	intentions, it is possible to check words against a corpus, and, in the
	case of a misspelled word, look for plausible corrections based on 
	edit distance.

	\textit{Whether to split multiple words.}  Although workers were 
	instructed to put one word per text input, many put multiple words.
	Theoretically the original multi-word entry might bear additional 
	information that could be useful in discerning a worker's exposure. 
	In practice, it would be necessary for that word combination to recur,
	which is unlikely.  Therefore we chose to split multi-word entries,
	using the individual words as features.  This meant that the outputs of
	some workers generated more features than those of others.

	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
	before providing them to the classifier.  For example, the words 
	``berries'' and ``berry'' only differ in number, but would normally be
	treated as completely different features.  Lemmatization ensures that
	nouns are in their sigular form, which helps to eliminate variations in
	labels that increase sparsity without conveying discriminative 
	information.

	\textit{Removal of stop-words.}  Certain very common words such as `the',
	``to'', and ``it'' are extremely common but don't help discriminate a 
	worker's exposure.  Removing these words is a common practice because
	they otherwise introduce noise into the classifier learning process.

	the were many
	missipellings

		\item{whether to split multiple words 
	\end{itemize}

	opt for a one-shot approach where we do not optimize any 
	\item{Adopting Naive Bayes due to the lack of optimization required.}
	\item{
		Usage of a principled set of pre-processing and representation 
		techniques.
	}
	\item{
		Comparison to other choices of representation
	}
	\item{
		Comparison to SVM classifier
	}
	\item{
		Reiterate why we cannot report optimized results.
	}
\end{itemize}
